%-------------------------
% Resume in Latex
% Author : Carl V. Lewis
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://carlvlewis.github.io}{\Large Carl V. Lewis}} & Email : \href{mailto:carl@carlvlewis.net}{carl@carlvlewis.net}\\
  \href{http://datastorytelli.ng}{https://carlvlewis.github.io} & Mobile : +1-912-816-7007 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Columbia University in the City of New York}{New York, NY}
      {Master of Science in Digital Media, Data Journalism;  GPA: Honors}{Aug. 2011 -- May 2012}
    \resumeSubheading
      {Mercer University}{Macon, GA}
      {Bachelor of Arts, Journalism and Media Studies; Bachelor of Arts, Southern Studies; GPA: 3.92}{Aug. '07 - May. '11}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Open Savannah, a Code for America Brigade}{Savannah, GA}
      {Founder, Brigade Captain}{Feb. 2017 - Present}
      \resumeItemListStart
        \resumeItem{Nonprofit Organization Leadership}
          {Founded civic-tech nonprofit, cultivated it into a nearly 200-person strong movement for more open and accessible government. Built out 10-person leadership team.}
      \resumeItemListEnd


          
    \resumeSubheading
      {cvl.digital}{Brooklyn, NY; Savannah, GA}
      {Owner/Operator}{Jul. 2014 - Present}
      \resumeItemListStart
        \resumeItem{Contract-Work}
          {I create magnetic digital work that distills information, sparks dialogue and elicits action, with a client focus on the nonprofit sector.}
      \resumeItemListEnd
      
      
          \resumeSubheading
  {St. Louis Post-Dispatch/stltoday.com}{St. Louis, MO}
      {Senior Editor for News Graphics}{May 2016 - Aug 2016}
      \resumeItemListStart
        \resumeItem{Data and Interactive Storytelling}
          {Coded and wrote data-driven news pieces, combining numbers with narrative to help bridge the gap between the abstraction of data and the empathy of story.}
      \resumeItemListEnd
      
      
    
    

    \resumeSubheading
      {Savannah Morning News/Morning News Media}{Savannah, GA}
      {Online News Editor, Digital Media Manager}{Aug. 2012 - Jan. 2014}
      \resumeItemListStart
        \resumeItem{Content Strategy}
          {Increased weekly social reach by neary 500 percent by end of time at company.
          Broke company record by achieving 7 million pageviews in less than two months on the job by producing interactive pieces.}
          \resumeItem{Growth-Hacking}
          {Developed and executed growth strategies for company-wide social media platforms to reach younger audiences. Increased weekly average social reach from 21,000 to an average of 375,000 by end date. Grew Facebook fans from approximately 8.5K to 24K. Monitored and responded to metrics.}
        \resumeItem{Product Development, Product Engineering}
          {Led native app development for iOS and Android platforms that netted more than 19K app downloads.}   \resumeItemListEnd
          
    \resumeSubheading
      {The Oxford Student (newspaper) at University of Oxford}{Oxford, UK}
      {News Editor, Hillary Term. Online Editor, Trinity Tern}{Aug 2010 - May 2011}
      \resumeItemListStart
        \resumeItem{News Writing, Editing, Development of Digital Presence}{Overhauled University's student newspaper; built new website for oxfordstudent.com; developed a digital-first content strategy.}
     
      \resumeItemListEnd



  \resumeSubHeadingListEnd
 
\section{Awards and Recognition}
  \resumeSubHeadingListStart
    \resumeSubItem{MJ Bear Innovation Fellow}
      {Online News Association, 2013}
    \resumeSubItem{Best Online News Project}
      {Georgia Press Association, 2014}
         \resumeSubItem{Social Media Engagement Excellence Award}{Morris Publishing Group, 2014}
          \resumeSubItem{Valerie B. Edmonds Research Award}{Mercer University, 2011.}
  \resumeSubHeadingListEnd
  
\section{Selected Open-Source Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{OpenProcure}
      {A project intended to collect data on discretionary and formal municipal procurement thresholds from U.S. cities and find baseline standards.}
    \resumeSubItem{dataviz.tools}
      {A curated collection of my favorite data visualization tools, which was featured at the top of ProductHunt.com.}
    \resumeSubItem{cvStrap}
      {A responsive, print-ready longform academic CV template for the JSONResume schema, allowing developers and academics to update their CVs using JSON alone.}
  \resumeSubHeadingListEnd




\section{Relevant Skills Summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Technologies}
        {JavaScript ES6 (React, Vue, d3.JS, JSON, Node.js), Flexbox, HTML5, Python (Django), R}}
      \item{
     \textbf{Skills}{: Data visualization, basic data science/ML, digital analytics, content strategy, Salesforce, MySQL}
    }
  \resumeSubHeadingListEnd


-------------------------------------------
\end{document}
